Performance of prediction models for opportunities for improvment in trauma care among women compared to men and across patient cohorts

### 2023-12-11 project-plan.Rmd
pre analysis

@@

The nature of this study is non-invasive. However, handling of registry data will constitute a risk for breach of patients integrity. The registry used in this study does contain personal identification. In order to minimize the risk of breach, patients have been anonymized after collection of data and been assigned a new identification number upon entry into dataset. Due to the nature of the patient population, patients have not consented previous to entry into the registry, thus, there is an opt out principle applied here. This is common with registry data in Sweden, and opens up opportunities for studies. In turn, more scientific knowledge has great potential for benefit, both on the societal scale, as well as the individual. Thus, the risk for the individual is compatibly small. Further, no data is presented of individual patients in the study, mitigating risk of violating personal integrity. The study has been granted ethical permit, with the record number 2021-02541 and 2021-03531.

>>>>

!Here, add explanation of what machine learning is, along with what has been done in regards to ML and trauma care thus far!

@@

The nature of this study is non-invasive. However, handling of registry data will constitute a risk for breach of patients integrity. The registry used in this study does contain personal identification. In order to minimize the risk of breach, patients have been semi-anonymized after collection of data and been assigned a new identification number upon entry into dataset. Due to the nature of the patient population, patients have not consented previous to entry into the registry, thus, there is an opt out principle applied here. This is common with registry data in Sweden, and opens up opportunities for studies. In turn, more scientific knowledge has great potential for benefit, both on the societal scale, as well as the individual. Thus, the risk for the individual is compatibly small. Further, no data is presented of individual patients in the study, mitigating risk of violating personal integrity. The study has been granted ethical permit, with the record number 2021-02541 and 2021-03531.
